---
title: ""
author: "Dafnie Jayne Benajiba"
date: "2024-10-29"
output: pdf_document
---

#a
```{r}
df <- data.frame(
  Respondents = 1:20,
  Sex = c(2, 2, 1, 2, 2, 2, 2, 1, 2, 1, 1, 2, 1, 2, 1, 2, 2, 2, 1, 2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 3, 3, 2, 1, 3, 1, 2, 3, 1, 2, 1),
  Persons_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_School = c(6, 4, 3, 1, 2, 1, 5, 3, 1, 2, 4, 2, 5, 2, 3, 1, 2, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 1, 1, 3, 1, 2, 3, 3, 2, 2, 2, 3, 1, 3, 3, 2, 2)
)

print(df)
```
#b The dataset includes 20 respondents, mostly female, with varied father occupations (farmer, driver, or other). Households typically have 5-8 members, with several siblings in school (1-6). Housing types range from wooden to concrete, with concrete being the most common.

#b
```{r}
str(df)
summary(df)
```

#c 
```{r}
mean_siblings <- mean(df$Siblings_at_School)
mean_siblings
```
#d
```{r}
first_two_rows <- df[1:2, ]
first_two_rows
```
#e

```{r}
extracted_rows <- df[c(3, 5), c(2, 4)]
extracted_rows

```

#F
```{r}
types_houses <- df$Types_of_Houses
types_houses
```
#G
```{r}
males_farmers <- df[df$Sex == 1 & df$Fathers_Occupation == 1, ]
males_farmers
```
#H
```{r}
females_with_siblings <- df[df$Sex == 2 & df$Siblings_at_School >= 5, ]
females_with_siblings
```
#2

```{r}
df = data.frame(Ints=integer(),
Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```

#3-B
```{r}
respondents_data <- read.csv("~/RBasics/CS101_DataScience/worksheet3b/HouseholdData.csv")
respondents_data
```
#3-B
```{r}
respondents_data$Sex <- factor(respondents_data$Sex, levels = c("Male", "Female"), labels = c(1, 2))
respondents_data$Sex

```
#3-C 
```{r}
respondents_data$Types.of.House <- factor(respondents_data$Types.of.House, levels = c("Wood", "Concrete", "Semi-concrete"), labels = c(1, 2, 3))
respondents_data$Types.of.House
```
#3-D 
```{r}
respondents_data$Father.s.Occupation <- factor(respondents_data$Father.s.Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))
respondents_data$Father.s.Occupation <- as.integer(respondents_data$Father.s.Occupation)
respondents_data$Father.s.Occupation
```
#3-E.
```{r}
females_driver <- respondents_data[respondents_data$Sex == 2 & respondents_data$Father.s.Occupation == 2, ]
females_driver
```
#3-F
```{r}
siblings <- respondents_data[respondents_data$Sibling.at.Home >= 5, ]
siblings
```
#4
The graph shows that from July 14 to July 21, 2020, negative tweets are consistently the highest, peaking on July 15 and 21. Positive tweets peak on July 18, while neutral tweets fluctuate, generally falling between negative and positive counts.